*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-07 Code/Manuscript_O2.Rmd
PUR edits

The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a wider plateau under 25 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G). In contrast, growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I). Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).  In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).  Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).

>>>>

The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR. Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).  MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I), with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
